Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-08-15 review_article.Rmd
correct spelling of choropleth in images

```{r chloropleth-grid-create, echo=FALSE, message=FALSE, eval = FALSE}
library(grid)
library(png)
library(gridExtra)

plot1 <- png::readPNG('cancer_map_images/chloropleths/1.png')
plot2 <- png::readPNG('cancer_map_images/chloropleths/14.chloropleth1.png')
plot3 <- png::readPNG('cancer_map_images/chloropleths/15.chloropleth.png')
plot4 <- png::readPNG('cancer_map_images/chloropleths/3.chloropleth.png')
plot5 <- png::readPNG('cancer_map_images/chloropleths/5.chloropleth.png')
plot6 <- png::readPNG('cancer_map_images/chloropleths/6.chloropleth.png')
plot6 <- png::readPNG('cancer_map_images/chloropleths/7.chloropleth.png')
plot7 <- png::readPNG('cancer_map_images/chloropleths/8.chloropleth.png')
plot8 <- png::readPNG('cancer_map_images/chloropleths/20.chloropleth1.png')
plot9 <- png::readPNG('cancer_map_images/chloropleths/21.chloropleth2.png')
plot10 <- png::readPNG('cancer_map_images/chloropleths/23.chloropleth.png')
plot11 <- png::readPNG('cancer_map_images/chloropleths/24.chloropleth.png')
plot12 <- png::readPNG('cancer_map_images/chloropleths/25.chloropleth.png')
plot13 <- png::readPNG('cancer_map_images/chloropleths/26.chloropleth.png')
plot14 <- png::readPNG('cancer_map_images/chloropleths/27.chloropleth.png')
plot15 <- png::readPNG('cancer_map_images/chloropleths/29.chloropleth.png')
plot16 <- png::readPNG('cancer_map_images/chloropleths/30.chloropleth.png')

chloropleth_grid <- gridExtra::grid.arrange(grid::rasterGrob(plot1),grid::rasterGrob(plot2), grid::rasterGrob(plot3), 
                        grid::rasterGrob(plot4), grid::rasterGrob(plot5), grid::rasterGrob(plot6),
                        grid::rasterGrob(plot7), grid::rasterGrob(plot8), grid::rasterGrob(plot9),
                        grid::rasterGrob(plot10),grid::rasterGrob(plot11), grid::rasterGrob(plot12), 
                        grid::rasterGrob(plot13), grid::rasterGrob(plot14), grid::rasterGrob(plot15), 
                        grid::rasterGrob(plot16), nrow=4)

@@

```{r chloropleth-grid-print, echo = FALSE}
knitr::include_graphics("figures/choropleth_grid.png")
```

>>>>

```{r choropleth-grid-create, echo=FALSE, message=FALSE, eval = FALSE}
library(grid)
library(png)
library(gridExtra)

plot1 <- png::readPNG('cancer_map_images/choropleths/1.png')
plot2 <- png::readPNG('cancer_map_images/choropleths/14.choropleth1.png')
plot3 <- png::readPNG('cancer_map_images/choropleths/15.choropleth.png')
plot4 <- png::readPNG('cancer_map_images/choropleths/3.choropleth.png')
plot5 <- png::readPNG('cancer_map_images/choropleths/5.choropleth.png')
plot6 <- png::readPNG('cancer_map_images/choropleths/6.choropleth.png')
plot6 <- png::readPNG('cancer_map_images/choropleths/7.choropleth.png')
plot7 <- png::readPNG('cancer_map_images/choropleths/8.choropleth.png')
plot8 <- png::readPNG('cancer_map_images/choropleths/20.choropleth1.png')
plot9 <- png::readPNG('cancer_map_images/choropleths/21.choropleth2.png')
plot10 <- png::readPNG('cancer_map_images/choropleths/23.choropleth.png')
plot11 <- png::readPNG('cancer_map_images/choropleths/24.choropleth.png')
plot12 <- png::readPNG('cancer_map_images/choropleths/25.choropleth.png')
plot13 <- png::readPNG('cancer_map_images/choropleths/26.choropleth.png')
plot14 <- png::readPNG('cancer_map_images/choropleths/27.choropleth.png')
plot15 <- png::readPNG('cancer_map_images/choropleths/29.choropleth.png')
plot16 <- png::readPNG('cancer_map_images/choropleths/30.choropleth.png')

choropleth_grid <- gridExtra::grid.arrange(grid::rasterGrob(plot1),grid::rasterGrob(plot2), grid::rasterGrob(plot3), 
                        grid::rasterGrob(plot4), grid::rasterGrob(plot5), grid::rasterGrob(plot6),
                        grid::rasterGrob(plot7), grid::rasterGrob(plot8), grid::rasterGrob(plot9),
                        grid::rasterGrob(plot10),grid::rasterGrob(plot11), grid::rasterGrob(plot12), 
                        grid::rasterGrob(plot13), grid::rasterGrob(plot14), grid::rasterGrob(plot15), 
                        grid::rasterGrob(plot16), nrow=4)

@@

```{r choropleth-grid-print, echo = FALSE}
knitr::include_graphics("figures/choropleth_grid.png")

```
